\documentclass[11pt,a4paper]{letter}
\usepackage{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{xcolor}

\begin{document}

\begin{letter}{Hiring Manager\\Verkada}

\opening{Dear Hiring Manager,}

I am writing to express my interest in the [PositionName] position listed at [CompanyName]. With a Master of Science in Engineering, specializing in Computer Science from Johns Hopkins University, and extensive experience as a Software Engineer with Cisco Systems Inc., I am excited about the opportunity to contribute to your team.

At Cisco, I developed backend services for a MERN-based application and led the design of a Scheduling and Governance System, demonstrating my ability to work with diverse technologies and improve system efficiencies. My role required a deep understanding of DevOps principles, CI/CD pipelines, and agile software development—skills I am eager to bring to your team.

My academic and research experience at Johns Hopkins University, focusing on Machine Learning, Deep Learning, and Computer Vision, has equipped me with a solid foundation in data science and AI. Projects like the FinSight AI Suite and Computational Drug Discovery have allowed me to apply this knowledge practically, developing solutions that leverage machine learning for predictive analytics and bioinformatics.

I am particularly drawn to [CompanyName] because of its commitment to [mention any known company values, initiatives, technologies, or projects], and I am enthusiastic about the opportunity to contribute to [specific project or product, if known]. My background in software engineering, paired with my passion for leveraging technology to solve complex problems, makes me a strong fit for this role.

Thank you for considering my application. I look forward to the opportunity to discuss how my education, experience, and skills could be beneficial to your team. I am available at your convenience for an interview.

\closing{Sincerely,}

\hspace{1cm}Tanay Nayak

\end{letter}
\end{document}
