%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article} % Reduced the base font size to 10pt

% Packages and other document configurations
% ... (Include all the packages and configurations from your template here)

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[margin=0.75in]{geometry} % Reduced margins to 0.5 inches all around

\input{glyphtounicode}
%----------FONT OPTIONS----------
% Include your font package here
%--------------------------------

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1 - #2} & \textit{\small #4}
      \def\temp{#3}%
      \ifx\temp\empty % Adjust the vertical space as needed
      \else
        \\
        \textit{\small#3}\\
      \fi
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
% \renewcommand{\familydefault}{\sfdefault}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Tanay Nayak} \\ \vspace{1pt}
    \small (667) 900-3506 $|$ \href{mailto:tnayak2@jhu.edu}{\underline{tnayak2@jhu.edu}} $|$ 
    Baltimore, MD $|$
    \href{https://www.linkedin.com/in/tanay-nayak/}{\underline{LinkedIn}} $|$
    \href{https://github.com/tanaynayak}{\underline{GitHub}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Johns Hopkins University}{Baltimore, MD}
      {Master of Science in Engineering, Computer Science}{2023 - 2025(Expected)}
    % Now add the details in a separate list right after the subheading
    \begin{itemize}
        \resumeItem{Relevant Courses: Software System Design, Machine Learning, Deep Learning, Computer Vision, Machine Translation, Natural Language Processing (NLP), Intro Algorithms.}
        \item Student Researcher at Laboratory of Computational Intensive Care Medicine employing unsupervised ML techniques to predict subphenotypes in Traumatic Brain Injury patients.
    \end{itemize}
    
    \resumeSubheading
      {Manipal Institute of Technology}{Manipal, India}
      {Bachelor of Technology, Computer Science and Engineering}{2017 - 2021}
    % Additional details for this entry
    \resumeItemListStart
        \resumeItem{Minor Specialization: Computational Mathematics.}
        \resumeItem{ Relevant Courses: Data Structures and Algorithms, Computer Architecture, Database Management, Software Testing.}
        \resumeItem{ Graduated with a CGPA of 8.63/10 with 9.5+ GPA (Certificate of Merit) in Senior Year.}
        \resumeItem{ Activities and Societies:}
        \begin{itemize}[label=\textopenbullet]
            \item {\small Treasurer and Head of Quizzing Society at the Literary, Debate and Quiz club}
            \item {\small Core committee member at ACM Manipal Chapter.}
        \end{itemize}
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages}{: Python, C/C++, Java, JavaScript} \\
     \textbf{Tools and Technologies}{: HTML/CSS/JS, DevOps, CI/CD, Linux (Bash Scripting), SQL, Node.js, MongoDB, React} \\
     \textbf{Data Science/AI}{: PyTorch, TensorFlow, Keras, Pandas, NumPy, Scikit-learn, Matplotlib, Seaborn, SciPy} \\
     \textbf{Other Skills}{: Statistics, Microsoft Office, Agile, Graphic Design (Adobe Photoshop/Illustrator)}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Cisco Systems Inc.}{Bangalore, India}
      {}{Feb 2021 - Jul 2023}
     \resumeSubSubheading
      {Software Engineer 2}{Sep 2022 - Jul 2023}
      \resumeItemListStart
        \resumeItem{Developed backend services for a MERN-based application, utilizing MongoDB and Kubernetes deployment.}
        \resumeItem{Spearheaded design and implementation of a Scheduling and Governance System leveraging Python, Bash, MS SQL, and AngularJS.}
        \resumeItem{Communicated product test data and efficiency improvement plans quarterly to stakeholders through interactive presentations.}
      \resumeItemListEnd

    \resumeSubSubheading
      % {Cisco Systems Inc.}{Bangalore, India}
      % {} {}
      {Software Engineer}{Aug 2021 - Aug 2022}
      \resumeItemListStart
        \resumeItem{Engineered a Continuous Deployment solution for global python package deployment, reducing production issues by 80\%.}
        \resumeItem{Established CI pipelines for continuous unit testing and code quality control using tools Pytest, PEP8, and SonarQube, improving testing efficiency and overall code readability for 75+ Cisco product families.}
      \resumeItemListEnd
    \resumeSubSubheading
      % {Cisco Systems Inc.}{Bangalore, India}
      {Technical Undergraduate Intern}{Feb 2021 – Aug 2021}
      \resumeItemListStart
        \resumeItem{Transitioned a monolithic Application (Test Code Manager) to microservices using Flask, Pytest, and Robot Framework.}
        \resumeItem{Deployed containerized python microservices on Kubernetes clusters, enabling a 50\% increase in deployment efficiency and ensuring 99.9\% uptime for critical applications.}
      \resumeItemListEnd

    \resumeSubheading
      {SAP Labs}{Bangalore, India}
      {iXp Intern}{May 2020 - Aug 2020}
      \resumeItemListStart
        \resumeItem{Created a subscription-based web application for aggregating internal incidents with email reports using Python and jQuery.}
        \resumeItem{Designed a front-end test automation suite for S4HANA's Quotation to Cash segment using Selenium, Protractor, and Jasmine.}
        \resumeItem{Collaborated with a global intern team on two microprojects: 'Drishti' – an app to assist the blind with digital payments and an integrated web application for the gamification of learning online courses.}
      \resumeItemListEnd

    \resumeSubheading
      {Flexmoney Technologies Pvt. Ltd}{Mumbai, India}
      {Intern}{May 2018 - Jul 2018}
      \resumeItemListStart
        \resumeItem{Conducted software testing and analysis for a Java-based financial web application, increasing bugs caught before production deployments by 30\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{FinSight AI Suite}}{ }
        \resumeItemListStart
            \resumeItem{Engineered a MERN-based Finance Dashboard App with ML predictions leveraging Vite, Redux Toolkit, Material UI, Recharts on the frontend, and Node.js, Express.js, MongoDB in the backend for predictive financial analytics.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\textbf{Bioinformatics – Computational Drug Discovery}}{ }
        \resumeItemListStart
            \resumeItem{Collected ChEMBL data and computed molecular descriptors to build QSAR models and deployed it as a predictive web application for AChE inhibitors.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Additional Sections-----------
% Here, you can add other sections as needed. For example, Certifications, Publications, Honors & Awards, etc.

\end{document}
